UAlberta FES style for Beamer \LaTeX

### 2024-03-13 presentations/cea_2022_deck.tex
cea
update

\usepackage{graphicx,hyperref,fes,url}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
%\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{multirow}
\usepackage{capt-of}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tikz}
\usepackage{hyperref}

@@

% Add a date and possibly the name of the event to the slides
%  - again first a short version to be shown at the bottom of each slide
%  - second the full date and event name for the title slide

\renewcommand{\(}{\begin{columns}}
\renewcommand{\)}{\end{columns}}
\newcommand{\<}[1]{\begin{column}{#1}}
\renewcommand{\>}{\end{column}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author[Short Name (U ABC)]{%
  \texorpdfstring{%
    \begin{columns}
      \column{.1\linewidth}
      \column{.4\linewidth}
      \centering
      Andrew Leach \\University of Alberta
      \column{.4\linewidth}
      \centering
      Blake Shaffer \\University of Calgary
      \column{.1\linewidth}
      \end{columns}
 }
 {Leach and Shaffer (2019)}
}
\date{\small May, 2019}
\frame[plain]{
  \titlepage
}

@@

\begin{frame}{Carbon Pricing Policy and Power Generation Sources}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
       {\includegraphics[width=.9\paperwidth]{../../alberta_power/gen_ghg_price.png}}; \vspace{1cm}
   \vfill
\end{frame}

\begin{frame}{Carbon Intensity of Alberta Power}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
       {\includegraphics[width=.9\paperwidth]{../../alberta_power/monthly_ghg_mwh.png}}; \vspace{1cm}
   \vfill
\end{frame}

@@

\begin{frame}{Secanell Group}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
      {\includegraphics[height=3in]{../../secanell_1}}; \vspace{1cm}
   \vfill
\end{frame}

@@

\begin{frame}{Secanell Group}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
      {\includegraphics[height=3in]{../../secanell_2}}; \vspace{1cm}
   \vfill
\end{frame}

@@

\begin{frame}{Secanell Group}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
      {\includegraphics[width=4.5in]{../../secanell_3}}; \vspace{1cm}
   \vfill
\end{frame}

>>>>

\usepackage{graphicx,hyperref,url,fes}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
%\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{multirow}
\usepackage{capt-of}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tikz}
\usepackage{hyperref}

@@

@@

\author[Short Name (U ABC)]{%
  \texorpdfstring{%
    \begin{columns}
      \column{.1\linewidth}
      \column{.4\linewidth}
      \centering
      Andrew Leach \\University of Alberta
      \column{.4\linewidth}
      \centering
      Blake Shaffer \\University of Calgary
      \column{.1\linewidth}
      \end{columns}
 }
 {Leach and Shaffer (2022)}
}
\date{\small May, 2019}
\frame[plain]{
  \titlepage
}

@@

\begin{frame}{Carbon Pricing Policy and Power Generation Sources}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
       {\includegraphics[width=.9\paperwidth]{../../alberta_power/images/gen_ghg_price.png}}; \vspace{1cm}
   \vfill
\end{frame}

\begin{frame}{Carbon Intensity of Alberta Power}
   \tikz [remember picture,overlay]
    \node[yshift=-.5cm,xshift=0cm] at (current page.center)
       {\includegraphics[width=.9\paperwidth]{../../alberta_power/images/monthly_ghg_mwh.png}}; \vspace{1cm}
   \vfill
\end{frame}

@@

@@

@@
